Inferring Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-10-02 doc/paper-lcr.tex
draft update

This fact makes gravitational lensing a potentially important source of
systematic error for any estimate of luminosity or distance, an issue addressed
for \eg type Ia supernovae by \citet[][]{Holz+Wald,Linder+Holz} and for high
redshift galaxies by \citet{Loeb} among others. In time delay lens cosmography
the effect can be particularly important. \citet{Suyu2010} found that  the
lensing effect of mass structures along the (unusually over-dense)  line of
sight to the quadruply-imaged radio source B1608$+$656, the so-called ``external
convergence,'' was the dominant source of uncertainty in the inferred
cosmological parameters.

How can we correct for the line of sight lensing error, and make accurate
measurements through the Universe? As \citeauthor{LH} noted, when inferring
global quantities (such as the cosmological parameters), averaging the results
from a large number of independent objects will tend to reduce the error, as the
ensemble-averaged convergence approaches zero for an unbiased sample
\citep{xxx}. If the sample is biased, however, some residual systematic error
will remain while the statistical uncertainty decreases -- and this will be the
case for any sample selected by the brightness of the lensed object, or any
other quantity that depends on $\xkappa$. The latter class includes time delay
lenses, which are detected based on the separation of their images, which
increases with $\kappa$. Large samples of lenses are expected to be discovered
in the next decade in ground-based optical imaging surveys
\citep{Oguri+Marshll2010} -- but these samples will be image separation-limited,
due to the surveys' relatively poor ($\sim 1$~arcsec) image quality. Some of the
current sample of known time delay lenses were detected in surveys like this: we
might expect them to be somewhat biased towards high values of $\xkappa$.

@@

These observational investigations have provided very useful insight into the
problem.  Coming from the opposite direction, large numerical simulations have
been used to predict, from first principles the distribution of likely
external shears and convergences along strong lens lines of sight. \todo{Phil}{More
needed here. Holder \& Schechter, Dalal \& Watson}. \citet{Hilbert++2009}
performed ray-tracing experiments through the Millenium Simulation, generating
a predicted $\xkappa$ at every position in a simulated sky. The first step
towards using this excellent calibration resource was taken by
\citet{Suyu++2010}, who selected Millenium lines of sight that a) were found
to contain a strong lens and b) had comparable apparent galaxy overdensity in
a 45 arcsec radius aperture down to $i < 24$. This overdensity could be
compared to the overdensity of the B1608$+$656 line of sight
\citep{Fass+Koop2010}, and hence an estimate of  $\Pr(\xkappa)$ could be
made.

@@

This paper is organized as follows. In~\Sref{sec:theory} we review the relevant
gravitational lensing theory, before introducing our simple reconstruction 
model in \Sref{sec:model}.  We then test this model in two phases: first, in
\Sref{sec:knownMh+z}, with known redshift and halo mass for every galaxy in a
lens field, in order to quantify the irreducible uncertainty due to unseen mass,
and second, in \Sref{sec:obsMstar+z}, with realistic observational uncertainties
on the field galaxies' stellar masses and redshifts. We then propagate all these
uncertainties through to the time delay distance in a toy sample of 100 lenses,
in \Sref{sec:distances}. We discuss our results in \Sref{sec:discuss} before
concluding in \Sref{sec:conclude}.

@@

Strong lenses sit in our real Universe -- they are not truely isolated;
there is some mass along the line of sight coming from intervening structures.
These structures may be physically associated with the lens e.g. other members
of a group or cluster, or they may be the result of chance alignments at any redshift. 
Whilst it is rare for three galaxies to line up well enough for both of the background sources
to be strongly lensed \citep{gavazzi2008,collett2012}, the shear scale of dark matter halos
makes a partial alignment -- with the additional structure acting as a weak lens -- 
a near certainty, indeed \citet{valewhite2003} and \citet{hilbert2007} find that there
are no empty lightcones in a realistic universe. These additional structures induce an external shear
which can be recovered in the mass-modelling of the lens, but they can also introduce a convergence that
is undetectable from the image positions, shapes and relative fluxes; {\it the mass sheet-degeneracy} \citep[see e.g.][for details]{Falco1985,Schneider2006}.

If the intrinsic source brightness changes, the observed brightness in each image does not change
simultaneously - there is a time delay, $\Delta t$, between the brightness change in
each image. Despite the invariance of the image positions and fluxes, under the addition
of an external convergence (and appropriate re-scaling of the lens potential) the relative Fermat potential between the images is {\it not}
invariant, and so the time delay changes. As such it is necessary to include $\kappax$
in the lens modelling, if cosmological parameters are to be estimated accurately and
precisely from observed time delays \citep{Suyu2010}.

@@

For mass-sheets that are physically associated with the lens galaxy, the mass sheet
 affects the stellar dynamics of the
lens galaxy, so dynamical observations can break the internal
mass-sheet degeneracy by providing an additional estimate of the lens galaxy's mass
\citep[e.g.,][]{citations}.

@@

Cosmological dark matter simulations have shown that dark matter
halos are well approximated by NFW profiles \citep{NFW1997}, with a density
profile given by
\be\label{eq:rhonfw}
\rho(r) = 
\frac{\rho_0}{\left(r/r_{s}\right)
\left(1+r/r_{s}\right)^{2}},
\ee
where $r_{s}$ is a characteristic radius of the cluster, representing where
the density slope transitions from $r^{-1}$ to $r^{-3}$. This radius is related
to the virial radius of the halo by $r_{s}~=~r_{200}/c$, where $r_{200}$ is the radius at 
which 
\be
\rho(r_{200}) = 200\rho_{{\mathrm{crit}}}(z), \text{ where } \rho_{\mathrm{crit}}(z) \equiv \frac{3H^{2}(z)}{8\pi G}
\ee
and $c$ is the concentration parameter, which can be estimated from the halo's mass,
using a mass--concentration relation. Typically more massive halos are less concentrated,
but there is some scatter; we use the relation of \citet{neto2007} to estimate $c$
from the mass enclosed within $r_{200}$, which we denote as $M_{200}$. The best fit relation of \citet{neto2007} is given by
\be
c_{200} = 4.67 (M_{200}/10^{14} h^{-1} \Msun)^{-0.11}.
\ee
$\rho_0$ is calculated from the critical density and concentration parameter:
\be
\rho_0 = \rho_{\mathrm{crit}}(z)\frac{200}{3}\frac{c^{3}}{\ln(1+c)-c/(1+c)}.
\ee

Unphysically, if one integrates the density profile of an NFW profile, the total mass is divergent.
Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
line of sight will also be divergant\footnote{At large radius, $\Sigma_{\rm
nfw} \propto R^{-2}$, but the differential number of halos centred within an
annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$,
so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which
diverges logarithmically}. Since infinite mass is unphysical, the profile must
be truncated at some point. \todo{Tom}{Add notes on previous truncation results}. Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{Nandra2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius. In \Sref{sec:knownMh+z} we investigate how different truncations affect the recovered total convergence for a line of sight, using the truncated NFW profile of \citet{BMO}
\be\label{eq:bmoprofile}
\rho(r) = 
\frac{\rho_{\rm NFW} (r)}{1+\left(r/r_{t}\right)^2},
\ee
which is the same as the NFW profile in the limit that the truncation radius, $r_t$ goes to infinity. The convergence and shear for the BMO profile are given in Appendix \ref{appendix:halos}.

@@

We choose 100000 lines of sight from random positions in the catalogue, and for each line of sight we reconstruct the
convergences from every halo within 5 arcminutes and compare the reconstructed
$\kapparec$ with those from the ray tracing results. The standard deviation on $\kapparay$-$\kapparec$ is
shown in Figure \ref{fig:ScattervsTruncation} as a function of the radius at which the halo is truncated.
 It is clear from Figure \ref{fig:ScattervsTruncation} 
that as long as the truncation is greater than a few virial radii, the choice of truncation
radius does not broadly affect the scatter on $\kapparay-\kapparec$; from now on we choose 
to truncate the halos at $5 \Rhalo$. Since $\sigma\left(\kapparay-\kapparec\right)$ does not go to
zero, it is clear that out halo based prescription does not perfectly replicate the n-body results, we refer to this
 as the intrinsic error of the prescription.
 The intrinsic error has a standard deviation of $\sigi \sim 0.018$, although
this figure is inflated by a few outliers in the tails of $\pr\left(\kapparay-\kapparec\right)$. Such outliers would 
likely be rejected by their reconstructed shear not matching the shear of the lens model 
(see \citet{Wong} for the practicalities of this);
 this makes our estimate of the intrinsic error pessimistic. We do not include any additional constraints on P($\kappax$), given prior knowledge of the external shear in this work.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{perfectc.eps}
\caption[Biased?]{$\sumkappah$ verses $\kapparay$ for 100000 reconstructed lines of sight. The points are put into bins of width 0.01 in $\kapparec$, except the last bin containing all reconstructions with $\kapparec>0.14$. The errorbars show the population standard deviation for each bin. Since all of the errorbars are consistant with zero, there is no evidence for $\kapparec$ being a biased estimator of $\kapparay$}
\label{fig:isitbiased}
\end{figure}

The intrinsic error between the results of the halo based prescription and the raytraced convergence is an unavoidable error, even with perfect knowledge of halo mass and position. Before investigating the errors caused by imperfect knowledge of halo mass and redshift, we investigate the errors induced by a magnitude limited reconstruction and a field of view limited reconstruction. The halos in our catalogue are given magnitudes by the semi-analytic model of \citet{SAM} and by applying magnitude cuts to our catalogue, we can investigate the scatter caused by unobserved halos. The majority of the convergence comes from halos with an $i$ magnitude between 18 and 24. Figure \ref{fig:magcut} shows that the width of $\kapparec-\kapparay$ decreases quickly between $i=18$ and $i=24$. Objects brighter than $i=18$ are either too rare or too close to the observer to make a significant contribution to the convergence. Objects fainter than $i=24$ are too small to be important unless they are extremely close to the line of sight where it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$ - it is likely that these ultra-faint halos (or substructures), the uncertain contribution of voids and halos deviating from our spherical truncated NFW profile are the three major sources of the scatter in $\kapparec-\kapparay$; a deeper survey will not be sufficient to decrease the size of this scatter. Since a large number of callibration lines of sight must be reconstructed to sample $\pr(\kappav)$, it may prove unrealistic to reconstruct the calibration lines of sight out to 5 arcminutes. Figure \ref{fig:radcut} shows the width of $\kapparec-\kapparay$ as a function of reconstruction radius; in almost all cases there is no significant contribution to $\kappa$ from halos that are centred more than 1 arcminute away, although large groups or clusters can sometimes still make a contribution as far out as four arcminutes. For the rest of this work we will continue to model all of the halos out to 5 arminutes with an $i$ magnitude greater than 26, although a reconstruction with fields going out to two arcminutes and down to $i=24$ would do almost as well.

\begin{figure}
\includegraphics[width=\columnwidth]{mag_scatter.eps}
\caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting $i$ band depth of the halo reconstruction - there is no significant improvement from including small halos with magnitudes less than $i=24$}
\label{fig:magcut}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{radius_scatter.eps}
\caption[radius cut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting radius (in arcminutes) beyond which halos are not reconstructed. The majority of the convergence comes from halos centred within an arcminute of the line of sight}
\label{fig:radcut}
\end{figure}

@@

We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{behroozi2010}. From this stellar mass we simulate 
an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by \comments{ the product of the galaxy stellar mass function (GSMF) of \citet{Fontana2006} and} a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$. Where a spectroscopic redshift exists stellar masses can be estimated with typical uncertainties of 0.15 dex \citep{xxx}, however with photometric redshifts stellar mass uncertainties are typically three times as large \citep{xxx}; we use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and $\sigma_{M_*}=0.45$ otherwise. \comments{The \citet{Fontana2006} GSMF is given by a Schechter function with redshift evolving parameters
\be
\label{eq:GSMF}
{\dee N \over \dee M_*} \propto \left(10^{(M_*-M_0(z))}\right)^{(1+\alpha(z))} \exp \left(-10^{(M_*-M_0(z))}\right)
\ee 
where $M_0(z)=11.16+0.17z-0.07z^2$ and $\alpha(z)=-1.18-0.082z$.} For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in the \MS catalogue

@@

The method we have outlined can also be used to estimate the external shear
along a line of sight. Shear is an observable that can be extracted from
strong lens modelling, however there is a degeneracy between internal and
external shear. Progress has been made in disentangelling external and
internal shear \citep[\eg][]{xxx} but there are still significant
uncertainties: \citet{Wong} attempted to match the shear from strong lens
models with a reconstruction of the local lens group environment, but found a
tension between the strong lens model and the reconstruction of the
environment. Since \citet{Wong} only reconstructed the local lens group,
rather than the full line of sight contribution, it is unclear whether the
external shear from lens models can be reconciled with a line of sight
reconstruction. {\it If} external shear can be measured, it provides an
additional constraint on which of the Millenium Simulation lines of sight are
similar to the reconstructed line of sight. \citet{Suyu2012b} found that for RXJ1131 combining shear constriants with galaxy number count overdensity, gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the PDFfrom number count overdensity alone, $\pr(\kappax|N_{45})$.

@@

\todo{Tom}{More on shear here.}

@@

\bibliographystyle{apj}
\bibliography{references}

>>>>

This fact makes gravitational lensing a potentially important source of
systematic error for any estimate of luminosity or distance, an issue addressed
for \eg type Ia supernovae by \citet[][]{Holz+Wald1998,Linder+Holz2004} and for high
redshift galaxies by \tom{which paper?} \citet{Loeb} among others. In time delay lens cosmography
the effect can be particularly important. \citet{Suyu++2010} found that  the
lensing effect of mass structures along the (unusually over-dense)  line of
sight to the quadruply-imaged radio source B1608$+$656, the so-called ``external
convergence,'' was the dominant source of uncertainty in the inferred
cosmological parameters.

How can we correct for the line of sight lensing error, and make accurate
measurements through the Universe? As \citeauthor{Linder+Holz2004} noted, when inferring
global quantities (such as the cosmological parameters), averaging the results
from a large number of independent objects will tend to reduce the error, as the
ensemble-averaged convergence approaches zero for an unbiased sample
\citep{xxx}. If the sample is biased, however, some residual systematic error
will remain while the statistical uncertainty decreases -- and this will be the
case for any sample selected by the brightness of the lensed object, or any
other quantity that depends on $\xkappa$. The latter class includes time delay
lenses, which are detected based on the separation of their images, which
increases with $\kappa$. Large samples of lenses are expected to be discovered
in the next decade in ground-based optical imaging surveys
\citep{Oguri+Marshall2010} -- but these samples will be image separation-limited,
due to the surveys' relatively poor ($\sim 1$~arcsec) image quality. Some of the
current sample of known time delay lenses were detected in surveys like this: we
might expect them to be somewhat biased towards high values of $\xkappa$.

@@

These observational investigations have provided very useful insight into the
problem.  Coming from the opposite direction, large numerical simulations have
been used to predict, from first principles the distribution of likely
external shears and convergences along strong lens lines of sight. \todo{Phil}{More
needed here. Holder \& Schechter, Dalal \& Watson}. \citet{Hilbert++2009}
performed ray-tracing experiments through the Millenium Simulation \citep{Springel++2005}, generating
a predicted $\xkappa$ at every position in a simulated sky. The first step
towards using this excellent calibration resource was taken by
\citet{Suyu++2010}, who selected Millenium lines of sight that a) were found
to contain a strong lens and b) had comparable apparent galaxy overdensity in
a 45 arcsec radius aperture down to $i < 24$. This overdensity could be
compared to the overdensity of the B1608$+$656 line of sight
\citep{Fassnact++2011}, and hence an estimate of  $\Pr(\xkappa)$ could be
made.

@@

This paper is organized as follows. In~\Sref{sec:theory} we review the relevant
gravitational lensing theory, before introducing our simple reconstruction 
model in \Sref{sec:model}.  We then test this model in two phases: first, in
\Sref{sec:knownMh+z}, with known redshift and halo mass for every galaxy in a
lens field, in order to quantify the irreducible uncertainty due to unseen mass,
and second, in \Sref{sec:obsMstar+z}, with realistic observational uncertainties
on the field galaxies' stellar masses and redshifts. \comments{We then propagate all these
uncertainties through to the time delay distance in a toy sample of 100 lenses,
in \Sref{sec:distances}.} We discuss our results in \Sref{sec:discuss} before
concluding in \Sref{sec:conclude}.

@@

Strong lenses sit in our real Universe -- they are not truely isolated;
there is some mass along the line of sight coming from intervening structures.
These structures may be physically associated with the lens e.g. other members
of a group or cluster, or they may be the result of chance alignments at any redshift. 
Whilst it is rare for three galaxies to line up well enough for both of the background sources
to be strongly lensed \citep{Gavazzi++2008,Collett++2012a}, the shear scale of dark matter halos
makes a partial alignment -- with the additional structure acting as a weak lens -- 
a near certainty, indeed \citet{Vale+White2003} and \citet{Hilbert++2007} find that there
are no empty lightcones in a realistic universe. These additional structures induce an external shear
which can be recovered in the mass-modelling of the lens, but they can also introduce a convergence that
is undetectable from the image positions, shapes and relative fluxes; {\it the mass sheet-degeneracy} \citep{Falco++1985}.

If the intrinsic source brightness changes, the observed brightness in each image does not change
simultaneously - there is a time delay, $\Delta t$, between the brightness change in
each image. Despite the invariance of the image positions and fluxes, under the addition
of an external convergence (and appropriate re-scaling of the lens potential) the relative Fermat potential between the images is {\it not}
invariant, and so the time delay changes. As such it is necessary to include $\kappax$
in the lens modelling, if cosmological parameters are to be estimated accurately and
precisely from observed time delays \citep{Suyu++2010}.

@@

For mass-sheets that are physically associated with the lens galaxy, the mass sheet
 affects the stellar dynamics of the
lens galaxy, so dynamical observations can break the internal
mass-sheet degeneracy by providing an additional estimate of the lens galaxy's mass
\citep[e.g.,][]{xxx}.

@@

Cosmological dark matter simulations have shown that dark matter
halos are well approximated by NFW profiles \citep{NFW}, with a density
profile given by
\be\label{eq:rhonfw}
\rho(r) = 
\frac{\rho_0}{\left(r/r_{s}\right)
\left(1+r/r_{s}\right)^{2}},
\ee
where $r_{s}$ is a characteristic radius of the cluster, representing where
the density slope transitions from $r^{-1}$ to $r^{-3}$. This radius is related
to the virial radius of the halo by $r_{s}~=~r_{200}/c$, where $r_{200}$ is the radius at 
which 
\be
\rho(r_{200}) = 200\rho_{{\mathrm{crit}}}(z), \text{ where } \rho_{\mathrm{crit}}(z) \equiv \frac{3H^{2}(z)}{8\pi G}
\ee
and $c$ is the concentration parameter, which can be estimated from the halo's mass,
using a mass--concentration relation. Typically more massive halos are less concentrated,
but there is some scatter; we use the relation of \citet{Neto2007} to estimate $c$
from the mass enclosed within $r_{200}$, which we denote as $M_{200}$. The best fit relation of \citet{Neto2007} is given by
\be
c_{200} = 4.67 (M_{200}/10^{14} h^{-1} \Msun)^{-0.11}.
\ee
$\rho_0$ is calculated from the critical density and concentration parameter:
\be
\rho_0 = \rho_{\mathrm{crit}}(z)\frac{200}{3}\frac{c^{3}}{\ln(1+c)-c/(1+c)}.
\ee

Unphysically, if one integrates the density profile of an NFW profile, the total mass is divergent.
Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
line of sight will also be divergant\footnote{At large radius, $\Sigma_{\rm
nfw} \propto R^{-2}$, but the differential number of halos centred within an
annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$,
so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which
diverges logarithmically}. Since infinite mass is unphysical, the profile must
be truncated at some point. \todo{Tom}{Add notes on previous truncation results}. Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{Nandra++2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius. In \Sref{sec:knownMh+z} we investigate how different truncations affect the recovered total convergence for a line of sight, using the truncated NFW profile of \citet{BMO}
\be\label{eq:bmoprofile}
\rho(r) = 
\frac{\rho_{\rm NFW} (r)}{1+\left(r/r_{t}\right)^2},
\ee
which is the same as the NFW profile in the limit that the truncation radius, $r_t$ goes to infinity. The convergence and shear for the BMO profile are given in Appendix \ref{appendix:halos}.

@@

We choose 100000 lines of sight from random positions in the catalogue, and for each line of sight we reconstruct the
convergences from every halo within 5 arcminutes and compare the reconstructed
$\kapparec$ with those from the ray tracing results. The standard deviation on $\kapparay$-$\kapparec$ is
shown in Figure \ref{fig:ScattervsTruncation} as a function of the radius at which the halo is truncated.
 It is clear from Figure \ref{fig:ScattervsTruncation} 
that as long as the truncation is greater than a few virial radii, the choice of truncation
radius does not broadly affect the scatter on $\kapparay-\kapparec$; from now on we choose 
to truncate the halos at $5 \Rhalo$. Since $\sigma\left(\kapparay-\kapparec\right)$ does not go to
zero, it is clear that out halo based prescription does not perfectly replicate the n-body results, we refer to this
 as the intrinsic error of the prescription.
 The intrinsic error has a standard deviation of $\sigi \sim 0.018$, although
this figure is inflated by a few outliers in the tails of $\pr\left(\kapparay-\kapparec\right)$. Such outliers would 
likely be rejected by their reconstructed shear not matching the shear of the lens model 
(see \citet{Wong++2011} for the practicalities of this);
 this makes our estimate of the intrinsic error pessimistic. We do not include any additional constraints on P($\kappax$), given prior knowledge of the external shear in this work.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{perfectc.eps}
\caption[Biased?]{$\sumkappah$ verses $\kapparay$ for 100000 reconstructed lines of sight. $\sumkappah$ traces $\kapparay$, but with a non-zero offset which is due to the negative connvergence from voids. At fixed $\sumkappah$ the scatter in $\kapparay$ grows with $\sumkappah$.}
\label{fig:isitbiased}
\end{figure}

The intrinsic error between the results of the halo based prescription and the raytraced convergence is an unavoidable error, even with perfect knowledge of halo mass and position. Before investigating the errors caused by imperfect knowledge of halo mass and redshift, we investigate the errors induced by a magnitude limited reconstruction and a field of view limited reconstruction. The halos in our catalogue are given magnitudes by the semi-analytic model of \citet{deLucia+Blaizot2007} and by applying magnitude cuts to our catalogue, we can investigate the scatter caused by unobserved halos. The majority of the convergence comes from halos with an $i$ magnitude between 18 and 24. Figure \ref{fig:magcut} shows that the width of $\kapparec-\kapparay$ decreases quickly between $i=18$ and $i=24$. Objects brighter than $i=18$ are either too rare or too close to the observer to make a significant contribution to the convergence. Objects fainter than $i=24$ are too small to be important, unless they are extremely close to the line of sight where it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$. It is likely that ultra-faint halos (or substructures), the uncertain contribution of voids and halos deviating from our spherical truncated NFW profile are the three major sources of the scatter in $\kapparec-\kapparay$; a deeper survey will not be sufficient to decrease the size of this scatter. Since a large number of callibration lines of sight must be reconstructed to sample $\pr(\kappav)$, it may prove unrealistic to reconstruct the calibration lines of sight out to 5 arcminutes. Figure \ref{fig:radcut} shows the width of $\kapparec-\kapparay$ as a function of reconstruction radius; in almost all cases there is no significant contribution to $\kappa$ from halos that are centred more than 1 arcminute away, although large groups or clusters can sometimes still make a contribution as far out as four arcminutes. For the rest of this work we will continue to model all of the halos out to 5 arminutes with an $i$ magnitude greater than 26, although a reconstruction with fields going out to two arcminutes and down to $i=24$ would do almost as well.

\begin{figure}
\includegraphics[width=\columnwidth]{mag_scatter.eps}
\caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting $i$ band depth of the halo reconstruction. $\kapparec$ is given by $\sumkappah-\kappav$, where $\kappav$ is a constant such that $\left\langle\kapparec\right\rangle=0$. The majority of the constraining power comes from reconstructing halos with magnitudes between $18<i<24$}
\label{fig:magcut}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{radius_scatter.eps}
\caption[radius cut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting radius (in arcminutes) beyond which halos are not reconstructed. The majority of the convergence comes from halos centred within an arcminute of the line of sight}
\label{fig:radcut}
\end{figure}

@@

We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{Behroozi++2010}. From this stellar mass we simulate 
an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by \comments{ the product of the galaxy stellar mass function (GSMF) of \citet{Fontana2006} and} a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$. Where a spectroscopic redshift exists stellar masses can be estimated with typical uncertainties of 0.15 dex \citep{xxx}, however with photometric redshifts stellar mass uncertainties are typically three times as large \citep{xxx}; we use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and $\sigma_{M_*}=0.45$ otherwise. \comments{The \citet{Fontana2006} GSMF is given by a Schechter function with redshift evolving parameters
\be
\label{eq:GSMF}
{\dee N \over \dee M_*} \propto \left(10^{(M_*-M_0(z))}\right)^{(1+\alpha(z))} \exp \left(-10^{(M_*-M_0(z))}\right)
\ee 
where $M_0(z)=11.16+0.17z-0.07z^2$ and $\alpha(z)=-1.18-0.082z$.} For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in the \MS catalogue

@@

The method we have outlined can also be used to estimate the external shear
along a line of sight. Shear is an observable that can be extracted from
strong lens modelling, however there is a degeneracy between internal and
external shear. Progress has been made in disentangelling external and
internal shear \citep[\eg][]{xxx} but there are still significant
uncertainties: \citet{Wong++2011} attempted to match the shear from strong lens
models with a reconstruction of the local lens group environment, but found a
tension between the strong lens model and the reconstruction of the
environment. Since \citet{Wong++2011} only reconstructed the local lens group,
rather than the full line of sight contribution, it is unclear whether the
external shear from lens models can be reconciled with a line of sight
reconstruction. {\it If} external shear can be measured, it provides an
additional constraint on which of the Millenium Simulation lines of sight are
similar to the reconstructed line of sight. \citet{Suyu++2012b} found that for RXJ1131 combining shear constriants with galaxy number count overdensity, gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the PDFfrom number count overdensity alone, $\pr(\kappax|N_{45})$.

@@

@@

%\bibliographystyle{apj}
%\bibliography{references}

\input{references.tex}
